Papers

### 2023-02-04 quarto/index.qmd
update

Hi! I'm happy to connect and discuss.
My team is hiring intern scientists
at our <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara office</a> or other global offices. Just email me.

@@

## Ph.D. Interns</a>

* <a href="https://sites.cc.gatech.edu/~jchen896/" target="_blank">Jiaao Chen</a> (2022)
* <a href="https://bcmi.sjtu.edu.cn/home/zhangzs/" target="_blank">Zhuosheng Zhang</a> (2022)
* <a href="https://sbmaruf.github.io/" target="_blank">M Saiful Bari</a> (2022)
* <a href="https://renshuhuai-andy.github.io/" target="_blank">Shuhuai Ren</a> (2022)
* <a href="https://htwang14.github.io/" target="_blank">Haotao Wang</a> (2021, 2022)
* <a href="https://shuaizhang.tech/" target="_blank">Shuai Zhang</a> (2019&ndash;2020)

>>>>

Hi! I'm happy to connect and discuss. Our office is at <a href="https://www.google.com/maps/place/2795+Augustine+Dr,+Santa+Clara,+CA+95054/@37.3835062,-121.9778599,17z/data=!3m1!4b1!4m5!3m4!1s0x808fc9f208b94da1:0xd2df9ae053c51af0!8m2!3d37.383502!4d-121.9756659" target="_blank">Santa Clara</a> in the San Francisco Bay Area. Just email me.

@@
